### 2018-10-11 tex/evaluation.tex
Update evaluation.
Version 1.1.

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
{\color{blue}In Spark with SCache, }
first we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.
{\color{blue}To verify the universality of Scache, we also implemented SCache on Hadoop MapReduce. We use Terasort to evaluate the performance of SCache on Hadoop MapReduce.}

@@

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS \footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
At last, we measure the overhead of weighted reservoir sampling. 
{\color{blue}In terms of universality, we implemented SCache on Hadoop MapReduce and Spark respectively. It can be proved that the optimization scheme provided by SCache can adapt to the current mainstream distributed DAG framework without a lot of change cost.}
In short, SCache can decrease ~$89\%$ time of Spark shuffle. Furthermore, SCache achieves a ~$75\%$ and ~$50\%$ improvement of reduce stage completion time respectively in simple DAG application and Terasort without introducing extra network traffic. More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 25\% and an average of 15\%}

@@

{\color{blue}
\subsection{Hadoop}

To prove SCache compatibility as a plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy job on Hadoop can still be optimized.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with input data size 384GB. Without SCache, Hadoop writes intermediate data locally in the Map phase. Hadoop began to shuffle in the reduce stage. Because the large amount of shuffle data reaches the network bottleneck, Hadoop needs to wait for network transfer in the front of reduce stage. This causes the CPU resources to be idle. As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching and pre-scheduling in the Map phase. This avoids the Reduce phase waiting for the shuffle data. Furthermore, pre-fetching  utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

>>>>

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.

@@

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS \footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
}
At last, we measure the overhead of weighted reservoir sampling. 
In short, SCache can decrease ~$89\%$ time of Spark shuffle. Furthermore, SCache achieves a ~$75\%$ and ~$50\%$ improvement of reduce stage completion time respectively in simple DAG application and Terasort without introducing extra network traffic. More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}

@@

{\color{blue}
\subsection{Hadoop Mapreduce with SCache}

To prove SCache compatibility as a cross-framework plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop Mapreduce without SCache writes intermediate data locally in the Map phase. The shuffle phase and reduce phase start simultaneously. Because the large amount of shuffle data reaches the network bottleneck, The beginning part of reduce needs to wait needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the Map phase. This avoids the Reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}
